TKT RNAseq Experiment: Differential Expression Analysis

### 2023-06-23 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
TKT app finished
added FxM Venn

library(edgeR)
library(plotly)
library(heatmaply)

@@

@@

                        GRxWT.MC = GRxWT.M2[row.names(cpmdata2),'FDR'],
                        GRxWT.MDf = GRxWT.MDf2[row.names(cpmdata2),'FDR'],
                        GRxWT.MOE = GRxWT.MOE2[row.names(cpmdata2),'FDR'])

@@

```{r echo = F, include = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}

Samples = row.names(groups2)[groups2$Sex =='M'
                            & groups2$Genotype == 'GR']

hmdata = cpmdata2[Comparisons2[[8]],Samples]

hmdata=hmdata[2500:3000,]

hmdata=hmdata[intersect(row.names(hmdata),row.names(cpmdata)),]

hmdata=cbind(hmdata, cpmdata[row.names(hmdata),colnames(hmdata)])

colnames(hmdata)[10:18] = paste0("Old.",colnames(hmdata)[10:18])

row.names(hmdata) = convert[row.names(hmdata)]

cpm.text = round(hmdata,1)
i=1
while(i<=ncol(cpm.text)){
  cpm.text[,i] = paste0("CPM: ", cpm.text[,i])
  i = i+1
}

  heatmaply(hmdata,
            trace="none",
            col=RdYlBu(100)[100:1],
            scale="row",
            dendrogram = "both",
            Rowv=T,
            Colv=T,
            cexRow = .75, 
            na.color="grey",
            cexCol = .75,
            labRow = as.character(row.names(hmdata)),
            key = T,
            column_text_angle = 90,
            ##col_side_colors=groups[Samples,1:3],
            ##col_side_palette=Spectral,
            main= "GR.FC x GR.FDf",
            custom_hovertext = cpm.text)

>>>>

library(edgeR)
library(plotly)
library(heatmaply)
library(VennDiagram)

@@

compare = makeContrasts(GR.F-GR.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
GR.FxM=DEout
sGR.FxM=DEout[DEout$FDR<.05,]

compare = makeContrasts(WT.F-WT.M, levels=design)
lrt = glmQLFTest(fit,contrast=as.vector(compare))
G_X_E<-topTags(lrt,adjust.method="BH",n = nrow(z$counts), sort.by="PValue")
DEout=G_X_E$table
WT.FxM=DEout
sWT.FxM=DEout[DEout$FDR<.05,]

@@

                        GRxWT.MC = GRxWT.M2[row.names(cpmdata2),'FDR'],
                        GRxWT.MDf = GRxWT.MDf2[row.names(cpmdata2),'FDR'],
                        GRxWT.MOE = GRxWT.MOE2[row.names(cpmdata2),'FDR'],

                        GR.FxM = GR.FxM[row.names(cpmdata2),'FDR'],
                        WT.FxM = WT.FxM[row.names(cpmdata2),'FDR'])

row.names(TKT.EdgeR2) = row.names(cpmdata2)

@@

```{r fig15, echo = F, fig.cap='Venn Diagram of total DEGs between male and female samples in a G85R and WT background.'}

GR.Up   = row.names(GR.FxM)[GR.FxM$logFC > 0 & GR.FxM$FDR <= .05]
GR.Down = row.names(GR.FxM)[GR.FxM$logFC < 0 & GR.FxM$FDR <= .05]
WT.Up   = row.names(WT.FxM)[WT.FxM$logFC > 0 & WT.FxM$FDR <= .05]
WT.Down = row.names(WT.FxM)[WT.FxM$logFC < 0 & WT.FxM$FDR <= .05]

##Sample titles as strings. Only fill in up to your number of selected categories
set1="G85R - F > M"
set2="G85R - M > F"
set3="WT - F > M"
set4="WT - F < M"

##items to be compared (ex: gene names) as a 1 dimensional vectors. Only give inputs up to your number of selected categories
s1=GR.Up
s2=GR.Down
s3=WT.Up
s4=WT.Down

#Quad Venn
grid.newpage()
tempvenn=draw.quad.venn(area1=length(s1),area2=length(s2),area3=length(s3),area4=length(s4), n12=length(intersect(s1,s2)),n13 = length(intersect(s1,s3)),n14 = length(intersect(s1,s4)),n23 = length(intersect(s2,s3)),n24 = length(intersect(s2,s4)),n34 = length(intersect(s3,s4)),n123 =  length(intersect(s1,intersect(s2,s3))),n124 =  length(intersect(s1,intersect(s2,s4))), n134 = length(intersect(s1,intersect(s3,s4))),n234 = length(intersect(s2,intersect(s3,s4))),n1234 = length(intersect(s1,intersect(s2,intersect(s3,s4)))),category =c(set1,set2,set3,set4),fill = c("blue", "red","green","yellow"),cex=2,cat.cex = 1)
